---
title: "Chicken Feed"
author: "put your name here"
date: "2/29/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

##  Chicken feed study  

data set has chicken weights and 4 variables:
  1.  chicken weight  
  2.  chicken feed type  
  3.  chicken time in the 40" run  
  4.  chicken sex   

Idea is to determine which of the variables affect chicken weight 
The weight and time to run are numerical variables, gender and feed type are categorical variables

So we'll use templatesRMD Cat Numerical, look for the section that has an 'aov'

<!-- This question is like a bunch of t-tests, but instead of doing the t-test a bunch of times we use ANOVA to do all the comparisons at once!  !-->

### get the data

```{r}
chickenData = read.csv('chickens.csv')
head(chickenData)
attach(chickenData)
```

### graphical summary

<!-- plot chicken weight against each of the three explanatory variables.  weight against a categorial varable is a boxplot, weight against a numerical variable is a scatter plot !-->





### Inference -- Analysis of Variance



###  Conclusions  -- which variables affect chicken weight?




### numerical summary
